---
title: "MPG Regression Analysis"
author: "Michael Garcia"
date: "2/18/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Executive Summary:
Motor Trend contains a vast amount of data relating to the vehicles specifications. The research will
attempt to answer two questions relating to our question: MPG is better

“Is an automatic or manual transmission better for MPG”
"Quantify the MPG difference between automatic and manual transmissions"



```{r cars}
summary(mtcars)
names(mtcars)
hist
```

## Exploratory Analysis


We will look at the distribution of the variables. 

```{r distribution, echo=FALSE}
mns = NULL
for (i in 1 : 1000) mns = c(mns, mean(runif(40)))5r
par(mfrow=c(2,2), mai = c(0.80, 0.80, 0.2, 0.1))
hist(mns, col = "dodger blue",breaks = 20, xlab = "simulated results")
rd <- runif(1000)
hist(rd,col = "green",breaks = 20, xlab = "uniform results")

abc <- function(x) dnorm(x, log = FALSE)
plot(abc, -max(mns), max(mns)
     #,main = "log { Normal density }"
     , xlab = "theoretical distribution")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
